MISUSES AND INACCURACY PATTERNS OF PAGEL'S LAMBDA ML ESTIMATION

### 2020-03-15 CoverPage-Evolution_EKB.Rmd
knit attempt - failed

---
title: A MULTIVARIATE EQUIVALENCY AND GENERAL TEST FOR RENSCH'S RULE: IMPLICATIONS FOR THE EVOLUTION OF SEXUAL SHAPE DIMORPHISM

@@

---
\begin{center}
\textbf{Dean C. Adams$^{1,*}$, Elizabeth Glynne$^{1}$ and Antigoni Kaliontzopoulou$^2$}
\end{center}

@@

$^{2}$CIBIO Research Centre in Biodiversity and Genetic Resources, InBIO, Universidade do Porto, Campus de Vairão. Vila do Conde, Portugal.

@@

\hfill\break
**Keywords**: Sexual dimorphism, multivariate, morphological evolution \hfill\break

**Short Title**: Multivariate Test of Rensch's Rule \hfill\break

**Author Contributions**: DCA devised the approach, AK provided the empirical example; all authors contributed  to all parts of this manuscript. \hfill\break

@@

**Acknowledgments**: We thank XXX for comments on drafts of this manuscript; Ana Perera, Inés Freitas and Daniele Salvi for the phylogeny reconstruction; and Chiara Ripa and Zélia Pereira for aiding shape data acquisition. This work was  sponsored in part by National Science Foundation Grant DBI-1902511 (to DCA), and by FEDER Funds through the Operational Competitiveness Factors Program - COMPETE and National Funds through FCT - Foundation for Science and Technology within the scope of the project “PTDC/BIA-EVL/28090/2017 - POCI-01-0145-FEDER-028090” (to AK).

>>>>

---
title: MISUSES AND INACCURACY PATTERNS OF PAGEL'S LAMBDA ML ESTIMATION

@@

---
\begin{center}
\textbf{Dean C. Adams$^{1,*}$ and Erica K. Baken$^{1}$}
\end{center}

@@

@@

\hfill\break
**Keywords**: Pagel's lambda, phylogenetic signal
\hfill\break

**Short Title**: Problems with Pagel's lambda \hfill\break

**Author Contributions**: DCA ...EKB...; all authors contributed  to all parts of this manuscript. \hfill\break

@@

**Acknowledgments**: We thank XXX for comments on drafts of this manuscript; ...... This work was  sponsored in part by National Science Foundation Grant DBI-1902511 (to DCA).
